### 2013-05-13 paper.tex
Writing more for the paper.

\subsection{Non-Dynamic Model}

@@

@@

\subsection{Computational Intractability of Computing Adversary's Target}

>>>>

\subsection{Simulating the Non-Dynamic Model}

@@

\subsection{Simulation Results}

We use the above model to simulate results, with $n = 100$, $\gamma = 250$, and $\kappa = 100$. In order words, we generate $\kappa = 100$ random graphs for each set of Erdos Renyi parameters, then on each graph, we run $\gamma = 250$ distinct infections which each start at a random node. The results are then summarized for different protection rates of $q$.

We begin by presenting the average infection probability $\hat{P}$ when the edge creation probability in Erdos Renyi is very small (we choose $p = 0.005$). Here the Erdos Renyi parameter is $np = 0.5$, which is below the threshold value for the existence of a giant component. Under this regime, the average infection probability $\hat{P}$ is very low for all protection levels (even a protection rate of $q = 0.05$).

The intuition behind this is clear. Since $np = 0.5 < 1$, the average size of a component is small, so the amount that the infection can spread is decreased. Thus, even for low protection rates, the infection cannot spread very far.

\begin{figure}
  \caption{Average Infection Rates for $np = 0.5 < 1$}
\end{figure}

When the Erdos Renyi parameter predicts the presence of a giant component, the average infection rate has a strong dependence on the protection rate. We use $np = 5 > 1$ which should produce a giant component with high probability, and simulate the resulting infection probabilities for various values of $q$. For low $q$, the average infection rate is incredibly high. For example, when $q = 0.05$, the average infection rate is $\hat{P} = 0.93$ with a standard deviation of $0.0103$.

However, as the protection rate increases, the average infection probability decreases almost linearly until about $q = 0.6$. Once $q = 0.6$, the positive externalities start to kick in and the average infection probability drops off more dramatically than the linear trend would predict. This can be attributed to the "network effect", or the extra benefit that everyone obtains from one person increasing their protection. Having higher $q$ will positively impact your neighbors because of the lower probability of you getting infected and thus transmitting to your neighbors.

\begin{figure}
  \caption{Average Infection Rates for $np = 5 > 1$}
\end{figure}

However, you must have enough connections in order for this network effect to become substantial. This is why the network effect does not manifest itself when there is no giant component. The figure below shows the network effect for different levels of $q$, where network effect $\nu$ is defined as follows:
\begin{eqnarray}
 \nu = 1 - q - \hat{P}
\end{eqnarray}

\begin{figure}
  \caption{Network Effect in a Giant Component ($np = 5$)}
\end{figure}

@@
